\Title

### 2020-12-16 manuscript/manuscript.tex
Minor tweaks to section about forward modeling by sum

We can improve the efficiency of the algorithm further by using only the $N_k$ data
points that fall within the $k$-th window for fitting the sources
(steps \ref{alg:scale} and \ref{alg:fit}),
while using all available data when calculating the step size and residuals
(steps \ref{alg:predicted}, \ref{alg:stepsize}, and \ref{alg:residual}).
By doing so, we reduce the Jacobian matrix further to $N_k \times M_k$
elements.
The forward modeling operations performed in steps \ref{alg:stepsize} and
\ref{alg:residual} can be done by a summation
(equation~\ref{eq:forward-sum})
instead of a matrix-vector product, which allows us to avoid computing and
storing the larger $N \times M_k$ Jacobian at any point.
The influence of distance sources on the solution is maintained by using the
entire set of data points when calculating
the step size $\alpha_k$ and updating the residuals vector.
In this case, the step size prevents the algorithm from worsening the fit to
data points that fall outside of the current window.
As such, it improves the converge of the solution and ensures that the
overall misfit decreases with iteration.

>>>>

We can improve the efficiency of the algorithm further by using only the $N_k$ data
points that fall within the $k$-th window for fitting the sources
(steps \ref{alg:scale} and \ref{alg:fit}),
while using all available data when calculating the step size and residuals
(steps \ref{alg:predicted}, \ref{alg:stepsize}, and \ref{alg:residual}).
By doing so, we reduce the Jacobian matrix further to $N_k \times M_k$
elements.
The forward modeling operation performed in step \ref{alg:predicted} can be
done by a summation (equation~\ref{eq:forward-sum})
instead of a matrix-vector product, which allows us to avoid computing and
storing the larger $N \times M_k$ Jacobian at any point.
The influence of distance sources on the solution is maintained by using the
entire set of data points when calculating
the step size $\alpha_k$ and updating the residuals vector.
In this case, the step size prevents the algorithm from worsening the fit to
data points that fall outside of the current window.
As such, it improves the converge of the solution and ensures that the
overall misfit decreases with iteration.
